---
title: "lab1"
author: "Jake Austin Kistler"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks

## Task 1
Get the working directory 

````{r}
# Return the wokring dir 
getwd()
````

## Task 2
Get the first 6 rows of data out of DDT.csv

````{r}
# Read in csv data into data
data <- read.csv("DDT-1.csv")

# display the first 6 rows of this data
head(data,6)
````

## Task 3
Subsetting Data:

Quanitiative  values: Mile, Length, Weight and DDT.

Qualititative values: River and Species.

Number of species in data set:
````{r}
# Return the number of 
length(unique(data$SPECIES))
````

Number of large mouth bass in sample with weights greater than 800 mg:
````{r}
# Extract data that has species as large maouth bass and weight greater than 800 mg
large_mouth_base_subset <- data[data$SPECIES == "LMBASS" & data$WEIGHT > 800, ]
# Display the data 
large_mouth_base_subset
````

Number of fish present in sample that came from the SMC river and had DDT values greater that 4.0:
````{r}
# Extract the data that has river of SCM and DDT values greater than 4.0
ddt_and_SMC_river <- data[data$RIVER == "SCM" & data$DDT > 4.0, ]
# Display the data
ddt_and_SMC_river
````

## Task 4

The mean (average) length of the fish in this data set:
```{r}
# Calculate and display the mean length of the fish in the data set
mean(data$LENGTH)
```

The standard deviation of the weight of the data set:
````{r}
# Calculate and display the standard div of the weight of the fish in the data set
sd(data$WEIGHT)
````

From the given picture we can recreate both potinal plots (WEIGHT vs LENGTH or LENGTH vs WEIGHT) to answer the question.
````{r}
# plot and display both graphs 
with(data, plot(WEIGHT ~ LENGTH, bg = "Orange", pch = 21, cex = 1))
with(data, plot(LENGTH ~ WEIGHT, bg = "Orange", pch = 21, cex = 1))
````
so given this information, the provided plot is the LENGTH vs WEIGHT or the first plot.

if v = 1:20 what is the last value of v/20?:
````{r}
# Create a vector with values 1 - 20 stored in it
v = 1:20
# divide each index by 20
v / 20
# The last value is 1.00 since it would be 20/20
````

## Task 5
Make a table of the rivers:
````{r}
river_table = with(data,table(data$RIVER))
river_table
````

A colored barplot of rivers:
````{r}
barplot(river_table, col = "brown")
````


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
