---
title: "lab1"
author: "Jake Austin Kistler"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks

## Task 1
Get the working directory 

````{r}
getwd()
````

## Task 2
Get the first 6 rows of data out of DDT.csv

````{r}
# Read in csv data into data
data <- read.csv("DDT-1.csv")

# display the first 6 rows of this data
head(data,6)
````

## Task 3
Subsetting Data:

Quanitiative  values: Mile, Length, Weight and DDT.

Qualititative values: River and Species.

Number of species in data set:
````{r}
length(unique(data$SPECIES))
````

Number of large mouth bass in sample with weights greater than 800 mg
````{r}
large_mouth_base_subset <- data[data$SPECIES == "LMBASS" & data$WEIGHT > 800, ]
large_mouth_base_subset
````

Number of fish present in sample that came from the SMC river and had DDT values greater that 4.0
````{r}
ddt_and_SMC_river <- data[data$RIVER == "SCM" & data$DDT > 4.0, ]
ddt_and_SMC_river
````


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
